---
title: "Larkin Secondary CREP"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 15)
```

## Libraries

```{r}
# library(rio)
library(lme4)
library(lmerTest)
library(MuMIn)
# library(plyr)
# library(psych)
# library(tidyr)
library(ggplot2)
library(dplyr)
# library(ggmosaic)
# library(MOTE)
# library(flextable)
# library(RColorBrewer)
```

## Import the Data

The `full_long` dataset includes all participants in long format - wherein each trial of their study is on one row of the dataset. This data has been merged with other relevant variables from the ACREP Turri Project found here: https://github.com/doomlab/CREP_Turri 

```{r}
load("../data/full_long.Rdata")
```

## Data Screening

- What, if any, rules for exclusion would you like to use? 

[89] "age_exclusion" - Age of majority    
[90] "previous_exclusion" - Previously participated 
[92] "studyans_exclusion" - Didn't answer all the questions correctly, or could use when they only get Darrel wrong
[93] "purpose_exclusion" - Guessed the purpose of the study
[95] "lang_exclusion" - Said their language wasn't good

```{r}
DF <- full_long %>% 
  filter(age_exclusion == FALSE) %>% 
  filter(previous_exclusion == FALSE) %>% 
  filter(purpose_exclusion == FALSE) %>% 
  filter(lang_exclusion == FALSE) %>% 
  filter(j_valid == TRUE) 
```

## Examine Data

```{r}
table(DF$j_expertise, 
      DF$vignette, 
      DF$j_cond,
      useNA = "ifany")

# only use darrel
DF <- DF %>% 
  filter(vignette == "Darrel") %>% 
  filter(!is.na(j_cond)) %>% 
  filter(!is.na(j_expertise))

# look at table
table(DF$j_expertise, 
      DF$j_cond,
      useNA = "ifany")

# look at the DVs
tapply(DF$j_know_vas, list(DF$j_expertise, DF$j_cond), mean, na.rm = T)
tapply(DF$j_know_vas, list(DF$j_expertise, DF$j_cond), sd, na.rm = T)
tapply(DF$j_know_vas, list(DF$j_expertise, DF$j_cond), function (x){sum(!is.na(x))})

tapply(DF$j_reason_vas, list(DF$j_expertise, DF$j_cond), mean, na.rm = T)
tapply(DF$j_reason_vas, list(DF$j_expertise, DF$j_cond), sd, na.rm = T)
tapply(DF$j_reason_vas, list(DF$j_expertise, DF$j_cond), function (x){sum(!is.na(x))})

tapply(DF$j_luck_vas, list(DF$j_expertise, DF$j_cond), mean, na.rm = T)
tapply(DF$j_luck_vas, list(DF$j_expertise, DF$j_cond), sd, na.rm = T)
tapply(DF$j_luck_vas, list(DF$j_expertise, DF$j_cond), function (x){sum(!is.na(x))})

DF %>% 
  group_by(j_expertise, j_cond, j_know_bin) %>% 
  count() %>% 
  na.omit()

DF %>% 
  group_by(j_expertise, j_cond, j_reason_bin) %>% 
  count() %>% 
  na.omit()

DF %>% 
  group_by(j_expertise, j_cond, j_luck_bin) %>% 
  count() %>% 
  na.omit()

DF$j_cond <- factor(DF$j_cond, 
                    levels = c("K", "G", "I"),
                    labels = c("Knowledge", "Gettier", "Ignorance"))
```

## VAS Analysis

### Knowledge VAS Analysis 

We will control for research lab using a multilevel model. We could also control for language, but lab also accounts for this variable. 

```{r}
know.model.1 <- lmer(j_know_vas ~ (1 | person_code),
                    data = DF, 
                    na.action = "na.omit")

know.model.2 <- lmer(j_know_vas ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    na.action = "na.omit")

AIC(know.model.1)
AIC(know.model.2) # lower = good

summary(know.model.2)
r.squaredGLMM(know.model.2)

hist(residuals(know.model.2))
{qqnorm(residuals(know.model.2)); abline(0,1)}
plot(residuals(know.model.2), scale(fitted(know.model.2)))
```

```{r}
ggplot(DF, aes(j_cond, j_know_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Knowledge Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))

ggsave("figures/fig_1.png", dpi = 300)
```

### Reasonable VAS Analysis

```{r}
reason.model.1 <- lmer(j_reason_vas ~ (1 | person_code),
                    data = DF, 
                    na.action = "na.omit")

reason.model.2 <- lmer(j_reason_vas ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    na.action = "na.omit")

AIC(reason.model.1)
AIC(reason.model.2) # lower = good

summary(reason.model.2)
r.squaredGLMM(reason.model.2)

hist(residuals(reason.model.2))
{qqnorm(residuals(reason.model.2)); abline(0,1)}
plot(residuals(reason.model.2), scale(fitted(reason.model.2)))
```

```{r}
ggplot(DF, aes(j_cond, j_reason_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Reasonable Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))

ggsave("figures/fig_2.png", dpi = 300)
```

### Luck VAS Analysis 

```{r}
luck.model.1 <- lmer(j_luck_vas ~ (1 | person_code),
                    data = DF, 
                    na.action = "na.omit")

luck.model.2 <- lmer(j_luck_vas ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    na.action = "na.omit")

AIC(luck.model.1)
AIC(luck.model.2) # lower = good

summary(luck.model.2)
r.squaredGLMM(luck.model.2)

hist(residuals(luck.model.2))
{qqnorm(residuals(luck.model.2)); abline(0,1)}
plot(residuals(luck.model.2), scale(fitted(luck.model.2)))
```

```{r}
ggplot(DF, aes(j_cond, j_luck_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Luck Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))

ggsave("figures/fig_3.png", dpi = 300)
```
## Forced Choice

### Knowledge Bin Analysis 

```{r}
know.model.1 <- glmer(j_know_bin ~ (1 | person_code),
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

know.model.2 <- glmer(j_know_bin ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

AIC(know.model.1)
AIC(know.model.2) # lower = good

summary(know.model.2)
r.squaredGLMM(know.model.2)
```

```{r}
tknow <- as.data.frame(table(DF$j_know_bin, DF$j_cond, DF$j_expertise))

colnames(tknow) <- c("knowledge_attribution", "j_condition", "Expertise", "Frequency")
tknow$Expertise <- factor(tknow$Expertise,
                          levels = c("naive", "expert"),
                          labels = c("Naive", "Expert"))

tknow %>% 
  ggplot(aes(fill = knowledge_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Knowledge Attribution by Condition and Expertise", fill="knowledge_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Knowledge Attribution", start = .9, end=0, labels = c("Believes", "Knows")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  

ggsave("figures/fig_4.png", dpi = 300)
```

### Reasonable Bin Analysis 

```{r}
reason.model.1 <- glmer(j_reason_bin ~ (1 | person_code),
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

reason.model.2 <- glmer(j_reason_bin ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

AIC(reason.model.1)
AIC(reason.model.2) # lower = good

summary(reason.model.2)
r.squaredGLMM(reason.model.2)
```

```{r}
treason <- as.data.frame(table(DF$j_reason_bin, DF$j_cond, DF$j_expertise))

colnames(treason) <- c("reasonable_attribution", "j_condition", "Expertise", "Frequency")
treason$Expertise <- factor(treason$Expertise,
                          levels = c("naive", "expert"),
                          labels = c("Naive", "Expert"))

treason %>% 
  ggplot(aes(fill = reasonable_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Reasonable Attribution by Condition and Expertise", fill="reasonable_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Reasonable Attribution", start = .9, end=0, labels = c("Reasonable", "Unreasonable")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  

ggsave("figures/fig_5.png", dpi = 300)
```

### Luck Bin Analysis 

```{r}
luck.model.1 <- glmer(j_luck_bin ~ (1 | person_code),
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

luck.model.2 <- glmer(j_luck_bin ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

AIC(luck.model.1)
AIC(luck.model.2) # lower = good

summary(luck.model.2)
r.squaredGLMM(luck.model.2)
```

```{r}
tluck <- as.data.frame(table(DF$j_luck_bin, DF$j_cond, DF$j_expertise))

colnames(tluck) <- c("luck_attribution", "j_condition", "Expertise", "Frequency")
tluck$Expertise <- factor(tluck$Expertise,
                          levels = c("naive", "expert"),
                          labels = c("Naive", "Expert"))

tluck %>% 
  ggplot(aes(fill = luck_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Ability/Luck Attribution by Condition and Expertise", fill="luck_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Ability/Luck Attribution", start = .9, end=0, labels = c("Ability", "Luck")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  

ggsave("figures/fig_6.png", dpi = 300)
```

## Combined Analyses

```{r}
DF$j_know_combined <- ifelse(
  DF$j_know_vas >= 55, "Knows", 
  ifelse(
    DF$j_know_vas <= 45, "Believes",
    NA
  )
)
DF$j_know_combined[DF$j_know_bin == "knows"] <- "Knows"
DF$j_know_combined[DF$j_know_bin == "believes"] <- "Believes"

DF %>% 
  group_by(j_expertise, j_cond, j_know_combined) %>% 
  count() %>% 
  na.omit()

DF$j_reason_combined <- ifelse(
  DF$j_reason_vas >= 55, "Reasonable", 
  ifelse(
    DF$j_reason_vas <= 45, "Unreasonable",
    NA
  )
)
DF$j_reason_combined[DF$j_reason_bin == "reasonable"] <- "Reasonable"
DF$j_reason_combined[DF$j_reason_bin == "Unreasonable"] <- "Unreasonable"

DF %>% 
  group_by(j_expertise, j_cond, j_reason_combined) %>% 
  count() %>% 
  na.omit()

DF %>% 
  group_by(j_expertise, j_cond, j_know_combined) %>% 
  count() %>% 
  na.omit()

DF$j_luck_combined <- ifelse(
  DF$j_luck_vas >= 55, "Ability", 
  ifelse(
    DF$j_luck_vas <= 45, "Luck",
    NA
  )
)
DF$j_luck_combined[DF$j_luck_bin == "luck"] <- "Luck"
DF$j_luck_combined[DF$j_luck_bin == "ability"] <- "Ability"

DF %>% 
  group_by(j_expertise, j_cond, j_luck_combined) %>% 
  count() %>% 
  na.omit()
```

### Knowledge Combined Analysis 

```{r}
DF$j_know_combined <- factor(DF$j_know_combined)

know.model.1 <- glmer(j_know_combined ~ (1 | person_code),
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

know.model.2 <- glmer(j_know_combined ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

AIC(know.model.1)
AIC(know.model.2) # lower = good

summary(know.model.2)
r.squaredGLMM(know.model.2)
```

```{r}
tknow <- as.data.frame(table(DF$j_know_combined, DF$j_cond, DF$j_expertise))

colnames(tknow) <- c("knowledge_attribution", "j_condition", "Expertise", "Frequency")
tknow$Expertise <- factor(tknow$Expertise,
                          levels = c("naive", "expert"),
                          labels = c("Naive", "Expert"))

tknow %>% 
  ggplot(aes(fill = knowledge_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Knowledge Attribution by Condition and Expertise", fill="knowledge_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Knowledge Attribution", start = .9, end=0, labels = c("Believes", "Knows")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  

ggsave("figures/fig_7.png", dpi = 300)
```

### Reasonable Bin Analysis 

```{r}
DF$j_reason_combined <- factor(DF$j_reason_combined)
reason.model.1 <- glmer(j_reason_combined ~ (1 | person_code),
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

reason.model.2 <- glmer(j_reason_combined ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

AIC(reason.model.1)
AIC(reason.model.2) # lower = good

summary(reason.model.2)
r.squaredGLMM(reason.model.2)
```

```{r}
treason <- as.data.frame(table(DF$j_reason_combined, DF$j_cond, DF$j_expertise))

colnames(treason) <- c("reasonable_attribution", "j_condition", "Expertise", "Frequency")
treason$Expertise <- factor(treason$Expertise,
                          levels = c("naive", "expert"),
                          labels = c("Naive", "Expert"))

treason %>% 
  ggplot(aes(fill = reasonable_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Reasonable Attribution by Condition and Expertise", fill="reasonable_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Reasonable Attribution", start = .9, end=0, labels = c("Reasonable", "Unreasonable")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition) 

ggsave("figures/fig_8.png", dpi = 300)
```

### Luck Bin Analysis 

```{r}
DF$j_luck_combined <- factor(DF$j_luck_combined)
luck.model.1 <- glmer(j_luck_combined ~ (1 | person_code),
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

luck.model.2 <- glmer(j_luck_combined ~ (1 | person_code) + j_cond*j_expertise,
                    data = DF, 
                    family = binomial,
                    na.action = "na.omit")

AIC(luck.model.1)
AIC(luck.model.2) # lower = good

summary(luck.model.2)
r.squaredGLMM(luck.model.2)
```

```{r}
tluck <- as.data.frame(table(DF$j_luck_combined, DF$j_cond, DF$j_expertise))

colnames(tluck) <- c("luck_attribution", "j_condition", "Expertise", "Frequency")
tluck$Expertise <- factor(tluck$Expertise,
                          levels = c("naive", "expert"),
                          labels = c("Naive", "Expert"))

tluck %>% 
  ggplot(aes(fill = luck_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Inability/Luck Attribution by Condition and Expertise", fill="luck_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Ability/Luck Attribution", start = .9, end=0, labels = c("Ability", "Luck")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  

ggsave("figures/fig_9.png", dpi = 300)
```